\documentclass[9pt]{../document-types/entcs} \usepackage{../document-types/entcsmacro}
\usepackage{graphicx}
\usepackage{tikz}
 \usepackage{mathtools}
 \usepackage{tabularx,lipsum,environ,amsmath,amssymb}
 \usepackage{diagbox}
\usetikzlibrary[shapes, arrows]
\usepackage{dot2texi}
\sloppy
% The following is enclosed to allow easy detection of differences in
% ascii coding.
% Upper-case    A B C D E F G H I J K L M N O P Q R S T U V W X Y Z
% Lower-case    a b c d e f g h i j k l m n o p q r s t u v w x y z
% Digits        0 1 2 3 4 5 6 7 8 9
% Exclamation   !           Double quote "          Hash (number) #
% Dollar        $           Percent      %          Ampersand     &
% Acute accent  '           Left paren   (          Right paren   )
% Asterisk      *           Plus         +          Comma         ,
% Minus         -           Point        .          Solidus       /
% Colon         :           Semicolon    ;          Less than     <
% Equals        =3D           Greater than >          Question mark ?
% At            @           Left bracket [          Backslash     \
% Right bracket ]           Circumflex   ^          Underscore    _
% Grave accent  `           Left brace   {          Vertical bar  |
% Right brace   }           Tilde        ~

% A couple of exemplary definitions:

\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}
\newcommand{\Nat}{{\mathbb N}}
\newcommand{\Real}{{\mathbb R}}
\definecolor{grena}{HTML}{971528}
\definecolor{nice}{HTML}{38b446}
\definecolor{warn}{HTML}{e2cb49}
\renewcommand{\P}{\textcolor{nice}{\textit{P}}}
\newcommand{\NPc}{\textcolor{grena}{\textit{NPc}}}
\newcommand{\?}{\textcolor{warn}{?}}
\def\lastname{Alves}
\begin{document}
\begin{frontmatter}
  \title{An Example Paper} \author{Matheus S. D'Andrea Alves\thanksref{ALL}\thanksref{myemail}}
  \address{Instituto de Computaç\~ao\\ Universidade Federal Fluminense\\
    Niter\'oi, Brazil} \author{U\'everton dos Santos Souza\thanksref{coemail}}
    \address{Instituto de Computaç\~ao\\ Universidade Federal Fluminense\\
      Niter\'oi, Brazil} \thanks[ALL]{Thanks
    to everyone who should be thanked} \thanks[myemail]{Email:
    \href{mailto:myuserid@mydept.myinst.myedu} {\texttt{\normalshape
        myuserid@mydept.myinst.myedu}}} \thanks[coemail]{Email:
    \href{mailto:couserid@codept.coinst.coedu} {\texttt{\normalshape
        couserid@codept.coinst.coedu}}}
\begin{abstract}
  This is a short example to show the basics of using the ENTCS style
  macro files.  Ample examples of how files should look may be found
  among the published volumes of the series at the ENTCS Home Page
  \texttt{http://www.elsevier.com/locate/entcs}.
\end{abstract}
\begin{keyword}
  Please list keywords from your paper here, separated by commas.
\end{keyword}
\end{frontmatter}





\section{Introduction}\label{intro}

\section{Começou}

{\sc Coloring($r,\ell$)} can be easily solved in polynomial time when $(r,\ell) \in \{(0,1),(1,0),(1,1),(2,0)\}$.
Therefore, in order to completely classify the complexity when $r+\ell \leq 2$ remains to analyse the $(0,2)$-case.

	\begin{lemma}
{\sc Coloring($0,2$)} can be solved in polynomial time.
\end{lemma}
	\begin{proof}
$(0,2)$-graphs, also known as co-bipartite, is a subclass of perfect graphs~\cite{bollo98}, consequently its chromatic number
equals to its clique number, which can be found in polinomial time using a polynomial algorithm for {\sc Independent Set}
on bipartite graphs (see~\cite{konig31,zing12}).
	\end{proof}

As $(3,0)$-graphs (tripartite graphs) have chromatic number at most three, and to verify if the chromatic number of a graph $G$
is one or two is trivial, we know that {\sc Coloring($3,0$)} can be solved in polynomial time.
Next we consider $(4,0)$-graphs.

\begin{lemma}
{\sc Coloring($4,0$)} is NP-Complete.
\end{lemma}
\begin{proof}
It is well-known that any planar graph is $(4,0)$ (4-colorable)~\cite{appel77}, and X and Y provide an $O(n^2)$ algorithm to find a 4-coloring of a planar graph.
In addition, to determine whether a planar graph $G$ is 3-colorable is NP-complete~\cite{larry} (even when a $(4,0)$-partition of $G$ is also provided).
Therefore to determine the chromatic number of $(4,0)$-graphs is NP-complete.
\end{proof}

Is noticeable that any $(r,\ell)$-graph is simultaneously a $(r+1,\ell)$-graph and a $(r,\ell+1)$-graph, since we can choose any vertex to act as both independent set and a clique. Therefore we can state that the problem is NP-Complete for any $(r,\ell)$-graphs $\forall r \geq 4 , \ell \geq 0$

The following theorem serves as base for the next demonstrations.

\begin{theorem}\label{list}
  {\sc List-Coloring$(r,\ell)$} is equivalent to {\sc Coloring$(r,\ell+1)$}.
\end{theorem}
\begin{proof}
    Let $G$ be the graph of an instance of {\sc List-Coloring$(r,\ell)$}, and $C=\{c_1,c_2,\ldots,c_n\}$ the color set formed by the lists of colors for each vertex.

    For each color $c_i \in C$ create a vertex $u_i$ and connects it to all others $u_j\; \forall j < i$. If a vertex $v \in V(G)$ does not have the color $c_i$ in its list, then adds an edge from $v$ to $u_i$. This steps generates a new graph $H$. It is simple to notice that if $H$ can be proper colored, then we found a solution to the {\sc List-Coloring} of $G$.

    The counterpart of the prof can be done by finding the maximum clique $Q$ of $H$ and building the color list of the remaining vertices $v$ as follow:

    $\forall u_i \in Q$ if $(v,u_i) \notin E(H)$ adds $c_i$ to the list of $v$. Note that $H\backslash Q = G$ and therefore a solution for {\sc List-Coloring} of $G$ can be easily extended to the {\sc Coloring} of $H$.
\end{proof}

Based in the previous demonstration we can extract the following corollaries

\begin{corollary}
  {\sc Coloring$(1,2)$} is NP-Complete.
\end{corollary}
\begin{proof}
  Derivates from the NP-Completeness of list coloring on split graphs \cite{jansen1997}.
\end{proof}

\begin{corollary}
  {\sc Coloring$(2,1)$ is Np-Complete.}
\end{corollary}
\begin{proof}
  Derivates from the NP-Completeness of bipartite graphs demonstrated by Fellows at \cite{fellows07}
\end{proof}

Now remain to us to demonstrate the complexity of {\sc Coloring(0,2)}. In order to do so we will use the following theorem, which is based on a theorem proposed by Jensen et.al \cite{jansen1999}. The proof is based on a reduction of the {\sc Restricted 3-SAT} problem to the {\sc List-Coloring(0,2)}

\textbf{Restricted 3-SAT}

\textbf{Given:} A set of unnegated variables $X = \{x_1,\ldots,x_n\}$ and negated variables  $\overline{X} = \{\overline{x}_1,\ldots,\overline{x}_n\}$, a collection of clauses $c_1,\ldots,c_m$ such that
\begin{itemize}
  \item each clause $c_i$ contains two or three different literals $y_{i,k} \in X \cup \overline{X}$
  \item there are at most three clauses that contain $x_j$ or $\overline{x}_j$ for each $1 \leq j \leq n$.
\end{itemize}

\textbf{Question:}  Does there exists a truth assignment for the variables such that each clause is satisfied?

\begin{theorem}
  {\sc List-Coloring(0,2) is Np-Complete}
\end{theorem}


\begin{proof}
Let $I$ be a instance of a restricted 3-SAT problem, we construct an instance $I'$ of list-coloring(0,2) problem as follows:

For each variable $j$ we create six vertices $a_j^{(1)}$, $a_j^{(2)}$, $a_j^{(3)}$;	$b_j^{(1)}$, $b_j^{(2)}$, $b_j^{(3)}$. each vertex has a color set as follow:
  \begin{itemize}
    \item $a_j^{(k)}$ := \{$j^{(k)}$, $\overline{j}^{(k)}$ \}
    \item $b_j^{(k)}$ := \{$\overline{j}^{(k)}$,$j^{((k \Mod{3}) + 1 )}$ \}
  \end{itemize}

Let $A$ be the set of all $a_j^{(k)}$ and $B$ the set of all $b_j^{(k)}$ build a clique with $A \cup B$.
Note that this clique can only be colored in two manners:
\begin{itemize}
	\item (1)  $f(a_j^{(k)}) = j^{(k)} => b_j^{(k)} = \overline{j}^{(k)}$
	\item (2)  $f(a_j^{(k)}) = \overline{j}^{(k)} => b_j^{(k)} = j^{((k \Mod{3}) + 1 )}$
\end{itemize}

Futhermore, for each clause create a vertex $c_i$ and populate their lists as follows:

For each variable $j$ or the negation of it $\overline{j}$ in the clause $i$, adds $j^{(k)}$ or $\overline{j}^{(k)}$ respectively to the list of $c_i$ where k is the current number of occurences of $j$. Since therae is at most three clauses with $j$ or $\overline{j}$ this assignment exists and can be found in polynomial time.

For example, let $I$ be the following Restricted 3-SAT:

$(p \lor q \lor r) \land (\neg{p} \lor q \lor r) \land (\neg{p} \lor \neg{r} \lor s)$

their clauses would be transformed in these vertex:

\begin{itemize}
	\item $c_1$ with list: \{$p^1$, $q^1$, $r^1$ \}
	\item $c_2$ with list: \{$\overline{p}^2$, $q^2$, $r^2$ \}
	\item $c_3$ with list: \{$\overline{p}^3$, $\overline{r}^3$, $s^1$ \}
\end{itemize}

		Let $C$ be the set containing all $c_i$ build a clique with $C \cup A$, obtaining a co-bipartite graph.

    Using the variable $p$ to demonstrate, if $p$ is {\sc true} then $a_p^{(1)},a_p^{(2)},a_p^{(3)}$ shall be colored with $\overline{p}^1,\overline{p}^2,\overline{p}^3$, allowing the color $p^x$,and denying the color $\overline{p}^x$ to be choosed to color a clause or another variable in the neighbourhood of $a_p^{(1)},a_p^{(2)},a_p^{(3)}$.

    Therefore is easy to see that if $I'$ can be list-colored then exists a truth assignment in $I$ that satisfies each clause. And that by construction if a thruth assignment satisfies $I$ then exists a list-coloring of $I'$ in the following way:

    \[color(a_j^{(k)})=
    \begin{cases}
       x_j^{(k)}, \text{if $x_j$ is false}\\
       \overline{x}_j^{(k)}, \text{otherwhise}
    \end{cases}
    \]

    \[color(b_j^{(k)})=
    \begin{cases}
      \overline{x}_j^{(k)}, \text{if $x_j$ is false} \\
       x_j^{((k \Mod{3}) + 1 )}, \text{otherwhise} \\
    \end{cases}
    \]

    \[color(c_i)= \text{any remaining color after the translate of assignment.}
    \]

\end{proof}

Using the reduction seen at theorem \ref{list} we obtain:

\begin{corollary}
  {\sc Coloring$(0,3)$} is NP-Complete.
\end{corollary}


Therefore we complete our dichotomy on the complexicity of {\sc Coloring$(r,\ell)$}:

\begin{table}[!h]
	\center
	\begin{tabular}{l|*{7}c}
		\toprule
		\backslashbox{$r$}{$\ell$} & 0 & 1 & 2 & 3 & 4 & \ldots & n\\
		\midrule
		0 & \P & \P & \P & \NPc & \NPc & \ldots & \NPc\\
		1 & \P & \P & \NPc & \NPc & \NPc & \ldots & \NPc\\
		2 & \P & \NPc & \NPc & \NPc & \NPc & \ldots & \NPc\\
		3 & \P & \NPc & \NPc & \NPc & \NPc & \ldots & \NPc\\
		4 & \NPc & \NPc & \NPc & \NPc & \NPc & \ldots & \NPc\\
		$\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\ddots$ & \NPc\\
		n & \NPc & \NPc & \NPc & \NPc & \NPc & \ldots & \NPc\\
		\bottomrule
	\end{tabular}%
	\caption{$\P/\NPc$ dichotomy on {\sc Coloring$(r,\ell)$}}
	\label{tab:tabela_dictrl}%
\end{table}%

\subsection{Peculiarity of {\sc Coloring$(2,1)$}}

Given any $(2,1)$ partitionable graph, to find the $(2,1)$ partition in which the clique is maximal is polynomial. Therefore a proper coloring can be made with $k +1$ colors where $k$ is the size of the clique. In other hand, as the clique has size $k$, we know that the coloring contains at least $k$ collors. Since {\sc Coloring$(2,1)$} $\propto$ {\sc List-Coloring$(2,0)$}, {\sc List-Coloring$(2,0)$} is NP-Complete. 

\section{Bibliographical references}\label{references}

\begin{thebibliography}{10}\label{bibliography}

\end{thebibliography}

\end{document}
